---
title: "Class06"
author: "Samuel Do (PID:A15803613)"
date: "2/3/2022"
output: pdf_document
---

# Exploring R functions

#Grade calculations
```{r}
#Input fectors
student1 <- c(100, 100, 100, 100, 100, 100, 100, 90)
student2 <- c(100, NA, 90, 90, 90, 90, 97, 80)
student3 <- c(90, NA, NA, NA, NA, NA, NA, NA)

```
```{r}
mean(student1)
mean(student2, na.rm = TRUE)
mean(student3, na.rm = TRUE)
```
#Determining function is.na()
```{r}
student2
is.na(student2)
```
#Use is.na() to get NA values and convert to zero
```{r}
student2[is.na(student2)] <- 0
student2
student3[is.na(student3)] <- 0
student3
```
#Use this logical to calculate now calculate grade
```{r}
mean(student1)
mean(student2)
mean(student3)
```
#Using min()/which.min() 
# min() finds lowest value
# which.min() finds location of lowest value in vector
```{r}
min(student1)
which.min(student1)
```
#Using this function to remove lowest grade
```{r}
student1[-which.min(student1)]
student2[-which.min(student2)]
student3[-which.min(student3)]
mean(student1[-which.min(student1)])
mean(student2[-which.min(student2)])
mean(student3[-which.min(student3)])
```
# Make function grade() to do this
# All R funcitons have 3 things
# Name(grade); Input Arguments(scores); body(does work)
```{r}
grade <- function(x, na.rm = FALSE) {x[is.na(x)] <- 0  
  mean(x[-which.min(x)]) }
grade(student1)
grade(student2)
grade(student3)
```
# Now use grade() on data set for assignment

# [Q1]Write a function grade() to determine an overall grade from a vector of student homework
assignment scores dropping the lowest single score. If a student misses a homework (i.e. has an NA value) this can be used as a score to be potentially dropped. Your final function should be adquately explained with code comments and be able to work on an example class gradebook
such as this one in CSV format: “https://tinyurl.com/gradeinput” 
```{r}
gradebook <- read.csv("https://tinyurl.com/gradeinput", row.names = 1)
head(gradebook)
```
#Now use apply() function to apply grade() to whole class
```{r}
apply(gradebook, 1, grade)
scores <- apply(gradebook, 1, grade)
```
# [Q2] Who is the top scoring student overall in the gradebook?
```{r}
which.max(scores)
max(scores)
```
# Student 18 has the highest score with a score of 94.5

# [Q3] Which homework was toughest on students?
```{r}
# apply() new function to get mean/median HW scores
HWmean <- apply(gradebook, 2, mean, na.rm = TRUE)
HWmean

HWmedian <- apply(gradebook, 2, median, na.rm = TRUE)
HWmedian
# Find minimum mean/median
which.min(HWmean)
min(HWmean)

which.min(HWmedian)
min(HWmedian)

```
# HW2 was the toughest since it had the lowest median score of 72.5, but HW3 could be considered the toughest since it had the lowest mean score of 80.8

# [Q4] Which HW correlates most with the average student score?
```{r}
gradebook2 <- gradebook
gradebook2[is.na(gradebook2)] <- 0
apply(gradebook2, 2, cor, scores)
```
# HW5 has the highest correlation to the student's average performance.

# [Q5]
# Select "Knit to Save"