---
title: "Class10"
author: "Samuel Do (PID:A15803613)"
date: "2/17/2022"
output: html_document
---

```{r}
#read genotype file\
mxl <- read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378.csv")
mxl
table(mxl$Genotype..forward.strand.)/nrow(mxl)
```

# Section 4: Population Scale Analysis

[Q13] Determine the sample size for each genotype and their corresponding median expression levels for each of these genotypes.
```{r}
expr <- read.table("rs8067378_ENSG00000172057.6.txt")
head(expr)
```
```{r}
nrow(expr)
table(expr$geno)
```
```{r}
summary(expr)
aggregate(x=expr$exp,
          by=list(expr$geno),
          FUN=median)
```

# The sample size for each genotype is as follows: There are 108 homozygous A/A samples, 233 heterozygous A/G samples, and 121 homozygous G/G samples. There are a total of 462 samples in this dataset. 
# The median expression levels for each genotype is as follows: The median expression level of A/A is 31.248, the median expression level of A/G is 25.065, and the median expression level of G/G is 20.074.


[Q14] Generate a boxplot with a box per genotype, what could you infer from the relative expression value between A/A and G/G displayed in this plot? Does the SNP effect the expression of ORMDL3?

```{r}
library(ggplot2)
ggplot(expr, aes(geno, exp, fill=geno)) + geom_boxplot(notch=TRUE) + xlab("Genotype") + ylab("Expression") + labs(title="Sample Genotype Expression")
```

# Because the first and third quartiles of the A/A and G/G samples do not overlap, there is no major overlap between the G/G samples and A/A samples' expression levels. Therefore, there is a significant difference in expression levels between the A/A and G/G samples, which means that the SNP does effect expression of ORMDL3. 
 